Automated Synthesis of State-Space Digital Controllers

### 2016-11-16 cav2017/cav2017.tex
more on solution generalisation

%-------------------------------
\section{Introduction}
%-------------------------------

@@

>>>>

%-------------------------------
\section{Introduction}
%-------------------------------
In this paper we formalise the notion of solution generalisation for CEGIS. 
This technique allows the inductive generalisation engine to look for 
candidate solutions in a reduced solution space.

@@

This technique relies on parametrising the target language, which
induces a lattice of progressively more expressive languages.  We
start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. As well as giving us an
automatic search procedure, this parametrisation greatly increases the
efficiency of our system since languages low down the lattice are very
easy to decide safety for (i.e. the validation oracle finds an answer
fast). If a program can be synthesised in a low-complexity language,
the whole procedure finishes much faster than if synthesis had been
attempted in a high-complexity language.
